---
title: "Getting started with lorentz.pj"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with lorentz.pj}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

Install the package from GitHub:

```{r eval=FALSE}
pak::pak("pjedyk/lorentz.pj")
```

## Overview

The `lorentz.pj` package provides tools for fitting Lorentzian curves
to spectroscopic data. The package includes:

- `lorentz_fit()` — fits a Lorentzian curve using nonlinear least squares
- `lorentz_predict()` — predicts values from a fitted model
- `lorentz_plot()` — visualizes the fit using [ggplot2](https://ggplot2.tidyverse.org/)

## Example: fitting spectroscopic data

```{r}
library(lorentz.pj)
data(spectra)
knitr::kable(head(spectra), caption = "First rows of the spectra dataset")
```

### Fitting the curve

```{r}
fit <- lorentz_fit(spectra$freq, spectra$readout)
fit$f0
fit$gamma
fit$r2
```

### Visualizing the result

```{r fig.width=6, fig.height=4}
lorentz_plot(fit)
```
